Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-03-03 manuscript/climate_sensitivity_draft.Rmd
removed CP acronymn
#82

Crown position ($CP$)--a categorical variable including dominant, co-dominant, intermediate, and suppressed--was recorded for all cored trees that remained standing during the growing season of 2018 following the protocol of @jennings_assessing_1999. While some trees undoubtedly changed position over the past several decades, in this case the bias would be unlikely to result in false acceptance of our hypothesis (i.e., type I error unlikely; type II error possible). An analysis of crown position relative to height (Fig. 2d) and height changes since the beginning of the study period indicated that changes between focal drought years (1966, 1977, and 1999; see below) were fairly small relative to differences among canopy positions (Fig. S3), with average tree height growth confined to ~0.82m from 1966 to 1977, ~1.45m from 1977 to 1999, and ~1.97m from 1999 to 2018. However, dominant and co-dominant trees were similar in height (Figs. 2d, S3).

@@

Crown position varied as expected with $H$ (dominant > co-dominant > intermediate > suppressed), but with substantial variation (Fig. 2d). Crown position was a much poorer predictor of $Rt$ than was $H$ in the single-variable tests (Table 4), lending little overall support to the hypothesis that crown exposure reduces $Rt$ (Table 1). When considered alone, $CP$ had a significant response only in the 1966 drought, during which trees with dominant $CP$ had the lowest $Rt$. When $H$ was included in the model, $CP$ was a significant predictor in the 1999 drought, with lowest $Rt$ for suppressed and then intermediate trees. Crown position was included in some of the full models (Table 5). In 1977, where $H$ was not included in the full model, dominant trees had the lowest $Rt$, and suppressed the highest. In contrast, in full models including both $H$ and $CP$ (all droughts and 1999), the lowest $Rt$ was in suppressed, followed by intermediate, trees.

>>>>

Crown position--a categorical variable including dominant, co-dominant, intermediate, and suppressed--was recorded for all cored trees that remained standing during the growing season of 2018 following the protocol of @jennings_assessing_1999. While some trees undoubtedly changed position over the past several decades, in this case the bias would be unlikely to result in false acceptance of our hypothesis (i.e., type I error unlikely; type II error possible). An analysis of crown position relative to height (Fig. 2d) and height changes since the beginning of the study period indicated that changes between focal drought years (1966, 1977, and 1999; see below) were fairly small relative to differences among canopy positions (Fig. S3), with average tree height growth confined to ~0.82m from 1966 to 1977, ~1.45m from 1977 to 1999, and ~1.97m from 1999 to 2018. However, dominant and co-dominant trees were similar in height (Figs. 2d, S3).

@@

Crown position varied as expected with $H$ (dominant > co-dominant > intermediate > suppressed), but with substantial variation (Fig. 2d). Crown position was a much poorer predictor of $Rt$ than was $H$ in the single-variable tests (Table 4), lending little overall support to the hypothesis that crown exposure reduces $Rt$ (Table 1). When considered alone, crown position had a significant response only in the 1966 drought, during which trees with dominant crown positiono had the lowest $Rt$. When $H$ was included in the model, crown position was a significant predictor in the 1999 drought, with lowest $Rt$ for suppressed and then intermediate trees. Crown position was included in some of the full models (Table 5). In 1977, where $H$ was not included in the full model, dominant trees had the lowest $Rt$, and suppressed the highest. In contrast, in full models including both height and crown position (all droughts and 1999), the lowest $Rt$ was in suppressed, followed by intermediate, trees.
